---
output: github_document
---

This is the README for the foofactors package. This is a toy package made for a course assignment. It is not recommended for general use. Instead use the forcats package. 

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# foofactors

The foofactors packages contains 4 functions to help make taking control of factors easier and less annoying. 

# To install

```{r}
devtools::install_github("ellenstephenson/foofactors")
library(foofactors)
```


# fbind()

`fbind()` combines two factors in a way that is more logical than c(a,b)

```{r}
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
c(a,b)
fbind(a,b)
```

# freq_out

To get a frequency table for the factor levels, use `freq_out()` function. 

```{r}
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
freq_out(x)
```


# levels_length

Factors that have only one entry for each level might be better left as character. `levels_length()` tests whether the number of levels is equal to the length of the factor. 

```{r}
x
levels(x)
length(x)
levels_length(x)

a
levels(a)
length(a)
levels_length(a)
```


# factor_levels

`factor()` will put the levels of the new factor in alphabetical order. `factor_levels` creates a factor where the levels are in the order they appear in the dataset. 

```{r}
time <- c("morning", "noon", "evening")
factor(time)
factor_levels(time)
levels(factor(time)) == time
```


